DATA 621 - Business Analytics and Data Mining

### 2020-11-22 Final_project/Draft_EDA_start.Rmd

Variables|Description   
-|----
views | The number of times a video was watched
category | the type of video, such as "Film & Animation", "Sports", "Music", etc... 
likes | the number of times a user clicked "like"
dislikes | the number of times a user clicked "dislike"
comment_count | the number of comments on an individual video   
comments_disabled | boolian value if the owner of the video disabled users from commenting   
ratings_disabled | boolian value if the owner of the video disabled ratings
country_code | code created to identify country of origin
view_target | Above (1) or below  (0) the mean views from country of origin
view_global_target | Above (1) or below  (0) the mean views globally

@@

ca_set <- ca_set%>%
  mutate(country = 'CA')%>%
  mutate(country_code = 1)%>%
  mutate(view_target = ifelse(views > ca_mean,1,0))
```

@@

de_set <- de_set%>%
  mutate(country = 'DE')%>%
  mutate(country_code = 2)%>%
  filter(complete.cases(de_set))%>%
  mutate(view_target = ifelse(views > de_mean,1,0))
```

@@

fr_set <- fr_set%>%
  mutate(country = 'FR')%>%
  mutate(country_code = 3)%>%
  filter(complete.cases(fr_set))%>%
  mutate(view_target = ifelse(views > fr_mean,1,0))
```

@@

gb_set <- gb_set%>%
  mutate(country = 'GB')%>%
  mutate(country_code = 4)%>%
  filter(complete.cases(gb_set))%>%
  mutate(view_target = ifelse(views > gb_mean,1,0))
```

@@

us_set <- us_set%>%
  mutate(country = 'US')%>%
  mutate(country_code = 5)%>%
  filter(complete.cases(us_set))%>%
  mutate(view_target = ifelse(views > us_mean,1,0))
```

```{r merge_datasets}
mergeCols = c('video_id','trending_date','title','channel_title','category_id','publish_time','tags','views','likes','dislikes','comment_count','thumbnail_link','comments_disabled','ratings_disabled','video_error_or_removed','description','country','country_code', 'view_target')

@@

```{r summary_ca}
summaryca <- ca_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryca)

@@

```{r summary_de}
summaryde <- de_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryus)

@@

```{r summary_us}
summaryus <- us_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryus)

@@

```{r summary_us}
summarygb <- gb_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summarygb)

@@

```{r summary_fr}
summaryfr <- fr_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryfr)

@@

```{r summary_global}
summarygl <- full_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summarygl)

@@

```{r}

>>>>

Variables|Description   
-|----
views | The number of times a video was watched
category | the type of video, such as "Film & Animation", "Sports", "Music", etc... 
likes | the number of times a user clicked "like"
dislikes | the number of times a user clicked "dislike"
comment_count | the number of comments on an individual video   
comments_disabled | boolian value if the owner of the video disabled users from commenting   
ratings_disabled | boolian value if the owner of the video disabled ratings
country_code | code created to identify country of origin
view_target | Above (1) or below  (0) the mean views from country of origin
view_global_target | Above (1) or below  (0) the mean views globally
tag_count | number of metadata tags applied to each video

@@

ca_set <- ca_set%>%
  mutate(country = 'CA')%>%
  mutate(country_code = 1)%>%
  mutate(view_target = ifelse(views > ca_mean,1,0))%>%
  mutate(tag_count = 1+(str_count(ca_set$tags, ';')))
```

@@

de_set <- de_set%>%
  mutate(country = 'DE')%>%
  mutate(country_code = 2)%>%
  filter(complete.cases(de_set))%>%
  mutate(view_target = ifelse(views > de_mean,1,0))%>%
  mutate(tag_count = 1+(str_count(de_set$tags, ';')))
```

@@

fr_set <- fr_set%>%
  mutate(country = 'FR')%>%
  mutate(country_code = 3)%>%
  filter(complete.cases(fr_set))%>%
  mutate(view_target = ifelse(views > fr_mean,1,0))%>%
  mutate(tag_count = 1+(str_count(fr_set$tags, ';')))
```

@@

gb_set <- gb_set%>%
  mutate(country = 'GB')%>%
  mutate(country_code = 4)%>%
  filter(complete.cases(gb_set))%>%
  mutate(view_target = ifelse(views > gb_mean,1,0))%>%
  mutate(tag_count = 1+(str_count(gb_set$tags, ';')))
```

@@

us_set <- us_set%>%
  mutate(country = 'US')%>%
  mutate(country_code = 5)%>%
  filter(complete.cases(us_set))%>%
  mutate(view_target = ifelse(views > us_mean,1,0))%>%
  mutate(tag_count = 1+(str_count(us_set$tags, ';')))
```

```{r merge_datasets}
mergeCols = c('video_id','trending_date','title','channel_title','category_id','publish_time','tags','views','likes','dislikes','comment_count','thumbnail_link','comments_disabled','ratings_disabled','video_error_or_removed','description','country','country_code', 'view_target','tag_count')

@@

```{r summary_ca}
summaryca <- ca_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summaryca)

@@

```{r summary_de}
summaryde <- de_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summaryus)

@@

```{r summary_us}
summaryus <- us_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summaryus)

@@

```{r summary_us}
summarygb <- gb_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summarygb)

@@

```{r summary_fr}
summaryfr <- fr_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summaryfr)

@@

```{r summary_global}
summarygl <- full_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summarygl)

@@
